\documentclass[11pt]{report}

% Packages
\usepackage[scaled]{helvet}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lipsum}
\usepackage{inconsolata}
\usepackage{enumitem}
\usepackage[dvipsnames]{xcolor}
\usepackage{setspace}

% Page Defaults
\renewcommand\familydefault{\sfdefault}
\pagenumbering{gobble}

% Variables
\def\dirname{fdr}
\def\docname{FDR}

\title{Test Plan - \docname}
\author{James Viner, Raymone Miller}
\date{} %Remove date
\begin{document}

\maketitle

\doublespacing

\pagebreak
\section*{Automated Test Cases}
Automated tests may be executed with {\texttt{\color{MidnightBlue}make check}}, which builds the executable and runs a bash script that performs unit testing for this program. Additional test details can be found in {\texttt{\color{MidnightBlue}test/test.bash}}; if the script does not run, check whether or not it is executable.
\pagebreak
\section*{Common Test Cases}
Prerequisites: {\texttt{\color{MidnightBlue}\dirname/}} directory does not already exist.
\subsection*{TC1: Installation}
\begin{enumerate}
  \item {\texttt{\color{MidnightBlue}git clone} {\color{MidnightBlue}git@git.umbc.tc}}{\color{MidnightBlue}:tdqc/tdqc12/jviner/\dirname.git}
  \item {\texttt{\color{MidnightBlue}cd \dirname}}
\end{enumerate}
\textbf{Expected:} {\texttt{\color{MidnightBlue}\dirname/}} directory is created.
\subsection*{TC2: Correct branch}
\begin{enumerate}
  \item {\color{MidnightBlue}git branch}
\end{enumerate}
\textbf{Expected:} {\color{MidnightBlue}main} is default branch.
\subsection*{TC3: Build cleaning}
\begin{enumerate}
  \item {\texttt{\color{MidnightBlue}make}}
  \item {\texttt{\color{MidnightBlue}make clean}}
  \item {\texttt{\color{MidnightBlue}ls}}
\end{enumerate}
\textbf{Expected:} No .o files or executable files are left in directory.
\pagebreak
\section*{Project-Building Test Cases}
Prerequisites: In the project's directory; have run {\texttt{\color{MidnightBlue}make clean}}.
\subsection*{TC4: Build Explicit}
\begin{enumerate}
  \item {\texttt{\color{MidnightBlue}make \dirname}}
  \item {\texttt{\color{MidnightBlue}ls \dirname}}
\end{enumerate}
\textbf{Expected:} File is listed.
\subsection*{TC5: Build Implicit}
\begin{enumerate}
  \item {\texttt{\color{MidnightBlue}make}}
  \item {\texttt{\color{MidnightBlue}ls \dirname}}
\end{enumerate}
\textbf{Expected:} File is listed.
\subsection*{TC6: Build debugging}
\begin{enumerate}
  \item {\texttt{\color{MidnightBlue}make debug}}
  \item {\texttt{\color{MidnightBlue}readelf --debug-dump=decodedline maze}}
\end{enumerate}
\textbf{Expected:} Debugging info is listed.
\subsection*{TC7: Build profiling}
\begin{enumerate}
  \item {\texttt{\color{MidnightBlue}make profile}}
\end{enumerate}
\textbf{Expected:} Program build output contains -gp flags.
\end{document}
